### 2025-07-24 README.Rmd
Modified timevarying options. No EWN

```{r,  echo=TRUE, eval=FALSE}
library(codeutils)
library(aMSE)

# ONCE AGAIN YOU WILL NEED TO SETUP YOUR OWN DIRECTORY STRUCTURE  TO DEFINE
# THE prefixdir
dropdir <-getDBdir()   
prefixdir <- pathtopath(dropdir,"/A_codeR/aMSETas/scenarios/")
filelist=c("controlEG.csv","lf_WZ90-20.csv","saudataEG.csv")
aMSE::copyto(prefixdir=prefixdir,fromdir="EG",todir="EGconst",
              filelist=filelist)
# this copies the files across and renames them appropriately.
# NO CHANGES ARE NEEDED IN THE FILES BECAUSE THE CHANGES OCCUR IN hsargs
```

@@

checkhsargs(hsargs)

>>>>

```{r,  echo=TRUE, eval=FALSE}
suppressPackageStartupMessages({
  library(aMSE)       # from github.com/haddonm/aMSE MSE codebase
  library(EGHS)       # from github.com/haddonm/EGHS example Tas harvest strategy
  library(codeutils)  # from github.com/haddonm/codeutils a set of code utilities
  library(hplot)      # from github.com/haddonm/hplot a set of plotting routines
  library(makehtml)   # from github.com/haddonm/makehtml used to display results
  library(knitr)      # from CRAN for generating tables
})
# ONCE AGAIN YOU WILL NEED TO SETUP YOUR OWN DIRECTORY STRUCTURE  TO DEFINE
# THE prefixdir
dropdir <-getDBdir()   
prefixdir <- pathtopath(dropdir,"/A_codeR/aMSETas/scenarios/")
filelist=c("controlEG.csv","lf_WZ90-20.csv","saudataEG.csv")
aMSE::copyto(prefixdir=prefixdir,fromdir="EG",todir="EGconst",
              filelist=filelist)
# this copies the files across and renames them appropriately.
# NO CHANGES ARE NEEDED IN THE FILES BECAUSE THE CHANGES OCCUR IN hsargs
```

@@

hsargs <- checkhsargs(hsargs)
